Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-23 chapters/introduction/introduction.tex
update approach

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  With the rough geographic location, we are able to refine the result
  with overhead images.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. 
  We present the algorithm details in \chapref{crosstransf}
  \newline

>>>>

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources fit best. For probabilistic outputs, we can also assign
  an energy score to each location and orientation combination
  according to how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline
